---
output: html_document
runtime: shiny_prerendered
---

```{r setup, echo = FALSE}
library(knitr)
library(tools)
opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  cache = TRUE)
```

## Seeing is Believing

```{r}
x <- rnorm(10)
mean(x)
```

Plain text about ...something... important.

Bulleted Lists

- SQL
- Python
- R

Numbered Lists (do not preserve the order of numbers that you input, instead shows 6, 7, 8)

6. SQL
1. Python
5. R

Tables

id | treatment
---| ---------
1  | control
2  | exclosure

# The Biggest Heading

## The Second Biggest Heading

### The Third Biggest Heading

## Chunks

```
The *emphasis* indicated by asterisks here does not become
italicized, as it would outside the "code fence".
```

```
seq(...)
```

## RMarkdown

```{r}
seq(1, 10)
```

## Chunk Options

```{r, echo = FALSE}
seq(1, 10)
```

## Chunk Labels

```{r does_not_run, eval = FALSE}
seq(1, 10)
```

## Sourced Input

```{r load_data, context = 'data', echo = FALSE, cache.extra = md5sum('worksheet-7.R')}
source('worksheet-7.R')
cty_to_cty <- subset(cty_to_cty, !is.na(movers_state_est))
```

```{r bar_plot}
library(ggplot2)
ggplot(state_movers,
  aes(
    x = reorder(current_state, -sum_new_movers), 
    y = sum_new_movers)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(
    angle = 90, hjust = 1))
```

## Alternative Engines

```{...}
greeting = 'Hello, {}!'
print(greeting.format('World'))
```

```{bash}
echo "Hello, ${USER}!"
```

## Cache Dependencies

```{r clean_bar_plot, dependson = 'load_data', echo = FALSE}
ggplot(state_movers,
  aes(
    x = reorder(current_state, -sum_new_movers), 
    y = sum_new_movers)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(
    angle = 90, hjust = 1))
```

## Input Objects

```{r, echo = FALSE}
selectInput('pick_state',
  label = 'Pick a State',
  choices = unique(cty_to_cty[['current_state']]))
```

```{r, context = 'server'}
library(dplyr)
output[['mov_plot']] <- renderPlot({
  cty_to_cty %>%
    filter(current_state == input[['pick_state']]) %>%
    group_by(prior_1year_state) %>%
    summarise(sum_new_movers = sum(movers_state_est, na.rm = TRUE)) %>%
    ggplot(aes(x = prior_1year_state, y = sum_new_movers)) +
    geom_bar(stat = 'identity') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
```


```{r, echo = FALSE}
plotOutput('mov_plot')
```

## Reactivity

```{r, context = 'server'}
plot_data <- reactive({
    filter(cty_to_cty, current_state == input[['pick_state']]) %>%
    group_by(prior_1year_state) %>%
    summarise(sum_new_movers = sum(movers_state_est, na.rm = TRUE))
})
output[['react_mov_plot']] <- renderPlot({
  plot_data() %>%
    ggplot(aes(x = prior_1year_state, y = sum_new_movers)) +
       geom_bar(stat = 'identity') +
       theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
```

```{r, echo = FALSE}
plotOutput('react_mov_plot')
```

## Lesson 7 exercises

Anna McPherran
July 24, 2019

**Exercise 1**

Create a table with two columns, starting with a header row with fields “Character” and “Example”. Fill in the table with rows for the special Markdown characters *, **, ^, and ~~, providing an example of each.

Character | Example
----------| ---------
*  | *italics*
**  | **bold**
^ | ^super^script
~~ | ~~strikethrough~~

**Exercise 2**

Display a copy of your presentation on GitHub. Your repository on GitHub includes a free web hosting service known as GitHub Pages. Publish your worksheet there with the following steps.